Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-22 General WLD combinatorics.tex
Few more changes to Lemma 3.7

We need a bit of notation:
Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.  Denote this diagram by $W_{[i,j]}$.

Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely $W_{[i,j+1]}$ and $W_{[j,i+1]}$.  Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.  In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously. \sanote{see e-mail about contracted WLD}

@@

We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
  %a configuration \eqref{eq:2 prop config} in $D$
or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item $q_r$ bounds a region of $W$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$. \sanote{so I understand, $q_r$ on the other side of $q_{r-1}$ than the $\{p_i\}$?} 
\end{itemize}
Since $W$ contains finitely many vertices, this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise. 
By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.  Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.

@@

Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$ not containing any $p_i$ for $i\leq r$.  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.

By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.  $W_r$ has no propagators of length $3$ since $W$ has none.  Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
%the configuration \eqref{eq:2 prop config}
then we are done, so assume otherwise.

@@

The overall result then follows by induction.

\note{The picture didn't apply any longer, but perhaps a new one would be nice?}
\end{proof}

>>>>

We need a bit of notation:
Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.  Denote this diagram by $W_{[i,j]}$. That is, if $W = (\cP, n)$ is a Wilson loop diagram, \bas W_{[i,j]} = (\cP \setminus \Prop([i,j]^c), n)\eas

{\color{blue} If we denote $Q = \Prop([i,j]^c)$, then we can write \bas M(W_{[i,j]}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$. That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$. } \sanote{If we like this idea, I can incorporate the necessary nomenclature earlier.}

Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely \bas W_{[i,j+1]} = W_{V_{in}(p, <_i) \cup V(p)} \quad \textrm{and} \quad  W_{[j,i+1]}  = W_{V_{out}(p, <_i) \cup V(p)} \eas corresponding to the regions inside and outside of $(p,<_i)$.  They contain the propagators on the inside and outside of $(p, <_i)$ respectfully, as well as $p$ itself.  We say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$ which we call outside and inside respectively. The ordering of the start and end points allow us to identify one or the other region unambiguously.

@@

We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
  %a configuration \eqref{eq:2 prop config} in $D$
or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item If we orient the $q_r$ such that the $\{p_1 \ldots p_r\}$ are on the inside. The outer region of $W$ that is bounded by $q_r$ is strictly contained in the region of $W$ bounded by $q_{r-1}$ on the outside. Thus the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$. \sanote{changed, have I broken it?}
\end{itemize}
Since $W$ contains finitely many vertices, this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise. 
By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.  Therefore there must exist a propagator $q_1$ outside of $(p_1, <_j)$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  This bounds a region $[i_1,k_1]$ on the outside (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.

@@

Now suppose $q_{r}$ exists by the induction hypothesis, oriented such that $(q_r, <_{k_r-1})$ and bounds a region $[i_r,k_r]$ on the outside. This region not containing any $p_i$ for $i\leq r$. \sanote{Know what $p_1$ is. What are the others?}  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.

By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.  $W_r$ has no propagators of length $3$ since $W$ has none.  Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
%the configuration \eqref{eq:2 prop config}
then we are done, so assume otherwise. \sanote{What if $p_{r+1}$ outside of $(q_r, <_{k_r-1})$?}

@@

The overall result then follows by induction.
\end{proof}
